---
title: "Visualize Data"
output:
  html_document:
    df_print: paged
    toc: TRUE
    toc_float: TRUE
    toc_depth: 4
    code_download: TRUE
---

```{r setup}
library(tidyverse)
```

```{r}
mpg
  
```


## Your Turn 1

Run the code on the slide to make a graph. Pay strict attention to spelling, capitalization, and parentheses!

```{r}
## Your Turn 1
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
  
```

## Your Turn 2

Add `color`, `size`, `alpha`, and `shape` aesthetics to your graph. Experiment.  

```{r}
## Your Turn 2
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = class))
  
```

## Your Turn 3

Replace this scatterplot with one that draws boxplots. Use the cheatsheet. Try your best guess.

```{r}
## Your Turn 3
ggplot(mpg) + 
  geom_boxplot(mapping = aes(x = class, y = hwy))
  
```

## Your Turn 4

Make a histogram of the `hwy` variable from `mpg`.

```{r}
## Your Turn 4
ggplot(data = mpg) +
  geom_histogram(mapping = aes(x = hwy), binwidth = 2)
  
```

## Your Turn 5

Make a density plot of `hwy` colored by `class`.

```{r}
## Your Turn 5
ggplot(data = mpg) +
  geom_density(mapping = aes(x = hwy, color = class))
  
```

## Your Turn 6

Make a bar chart `hwy` colored by `class`.

```{r}
## Your Turn 6
ggplot(data = mpg) +
  geom_bar(mapping = aes(x = class, fill = class))
  
```

## Your Turn 7

Predict what this code will do. Then run it.

```{r}
## Your Turn 7
ggplot(mpg) + 
  geom_point(aes(displ, hwy)) +
  geom_smooth(aes(displ, hwy))
  
```

## Your Turn 9

Save the last plot and then locate it in the files pane.

```{r, eval = FALSE}
## Your Turn 9
ggsave("my-plot.png")
  
```

*** 
## Appendix 1 - all code used in this training
```{r, ref.label=knitr::all_labels(),echo=TRUE, eval=FALSE}
```

***
## Appendix 2 - R Session Information

```{r}
sessionInfo()
```

