---
title: "Tidy Data"
output:
  html_document:
    df_print: paged
    toc: TRUE
    toc_float: TRUE
    toc_depth: 4
    code_download: TRUE
---

```{r setup}
library(tidyverse)
library(babynames)

# Toy data
cases <- tribble(
  ~Country, ~"2011", ~"2012", ~"2013",
      "FR",    7000,    6900,    7000,
      "DE",    5800,    6000,    6200,
      "US",   15000,   14000,   13000
)

pollution <- tribble(
       ~city, ~size, ~amount,
  "New York", "large",      23,
  "New York", "small",      14,
    "London", "large",      22,
    "London", "small",      16,
   "Beijing", "large",     121,
   "Beijing", "small",     121
)

x <- tribble(
  ~x1, ~x2,
  "A",   1,
  "B",  NA,
  "C",  NA,
  "D",   3,
  "E",  NA
)

# To avoid a distracting detail during class
names(who) <- stringr::str_replace(names(who), "newrel", "new_rel")
```

## Your Turn 1

On a sheet of paper, draw how the cases data set would look if it had the same values grouped into three columns: **country**, **year**, **n**

## Your Turn 2

Use `pivot_longer()` to reorganize `table4a` into three columns: **country**, **year**, and **cases**.

```{r}
## Your Turn 2
table4a %>% 
  pivot_longer(-country, 
								names_to = "year", values_to = "count")

```

## Your Turn 3

On a sheet of paper, draw how this data set would look if it had the same values grouped into three columns: **city**, **large**, **small**

## Your Turn 4

Use `pivot_wider()` to reorganize `table2` into four columns: **country**, **year**, **cases**, and **population**.

```{r}
## Your Turn 4
table2 %>% 
  pivot_wider(names_from = type,
								values_from = count)

```

## Your Turn 5

Pivot the 5th through 60th columns of `who` into a key column: value column pair named **codes** and **n**. Then select just the `county`, `year`, `codes` and `n` variables.

In the R code chunks below I have used the `head()` function as the datasets are generally 
large. This reduces the size of the output HTML file. The solution to the Your Turn example
will not require the use of `head()`.

```{r}
## Your Turn 5
who %>%
  pivot_longer(cols = 5:60, names_to="codes", values_to="n") %>%
  select(-iso2, -iso3) %>%
  head()

```

## Your Turn 6

Separate the `sexage` column into **sex** and **age** columns.

```{r}
## Your Turn 6
who %>%
 pivot_longer(cols = 5:60, names_to="codes", values_to="n") %>%  
 select(-iso2, -iso3) %>%
 separate(codes, c("new", "type", "sexage"), sep = "_") %>%
 select(-new) %>%
 separate(sexage, into = c("sex", "age"), sep = 1) %>%
  head()

```

## Check your understanding

Reshape the layout of this data. Calculate the percent of male (or female) children by year. Then plot the percent over time.

```{r}
## Check your understanding
babynames %>%
  group_by(year, sex) %>% 
  summarise(n = sum(n)) %>%
  pivot_wider(names_from = sex, values_from = n) %>%
  mutate(percent_male = M / (M + F) * 100) %>%
  ggplot(aes(year, percent_male)) + geom_line()

```

*** 
## Appendix 1 - all code used in this training
```{r, ref.label=knitr::all_labels(),echo=TRUE, eval=FALSE}
```

***
## Appendix 2 - R Session Information

```{r}
sessionInfo()
```