---
title: "Data Types"
output:
  html_document:
    df_print: paged
    toc: TRUE
    toc_float: TRUE
    toc_depth: 4
    code_download: TRUE
---

```{r setup}
library(tidyverse)
library(babynames)
library(nycflights13)
library(stringr)
library(forcats)
library(lubridate)
library(hms)
```

## Your Turn 1

Use `flights` to create `delayed`, the variable that displays whether a flight was delayed (`arr_delay > 0`).

Then, remove all rows that contain an NA in `delayed`. 

Finally, create a summary table that shows:

1. How many flights were delayed  
2. What proportion of flights were delayed

```{r}
## Your Turn 1
flights %>%
  mutate(delayed = arr_delay > 0) %>%
  drop_na(delayed) %>%
  summarise(total = sum(delayed), prop = mean(delayed))

```


## Your Turn 2
In the next few examples we're going to clean up a vector of treatment labels.
Let's first read the data so we can see what we're going to work with:
```{r}
## Your Turn 2
myTrts <- readRDS("Treatment_label_example.rds")
myTrts
```

We (humans) can see that "examplumab" is equivalent to "EXAMPLUMAB" and that 
maybe "Egmb" is a contraction of that treatment, but R cannot. There is also
quite a lot of dosing information that we should probably tidy so that we 
can extract information like the total daily dose.

When cleaning character strings, it's easier to do many steps cleaning one thing
at a time, rather than try to do it all at once. Use the functions below to 
clean up the treatment information above, checking at each stage that you have
extracted the information you expect.

Try to answer this question: How many distinct treatments are there?

```{r}
str_sub( start = , end = )
str_detect(pattern = )
word(start =  , end =  , sep = " ")
str_extract(pattern = )
str_replace(pattern =  , replacement =  )
str_replace_all(pattern =  , replacement =  )
str_subset(pattern = )

myTrts <- myTrts %>%
  
  
```

## Your Turn 2 and a bit

Use regular expressions to subset out the treatment doses that have decimal places.
(HINT: regex pattern \\d finds numeric values. Regex `+` 

But see also 
https://stringr.tidyverse.org/articles/regular-expressions.html) 

```{r}
## Your Turn 2 and a bit
myTrts %>%
  str_subset(pattern = "\\d+\\.+\\d+")

```

## Your Turn 3

Make a sensible graph of average TV consumption by marital status using the 
functions below and code template used in the slides for the `relig` factor.

```{r}
## Your Turn 3
gss_cat %>%
  drop_na(age) %>%
  group_by(age, marital) %>%
  count() %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(age, prop,color = fct_reorder2(marital, age, prop))) +
    geom_line()

```

## Your Turn 4

Do you think liberals or conservatives watch more TV?
Compute average tv hours by party ID an then plot the results.

```{r}
## Your Turn 4
gss_cat %>%
   drop_na(tvhours) %>%
    mutate(partyid = fct_recode(partyid,
    "Republican, strong"    = "Strong republican",
    "Republican, weak"      = "Not str republican",
    "Independent, near rep" = "Ind,near rep",
    "Independent, near dem" = "Ind,near dem",
    "Democrat, weak"        = "Not str democrat",
    "Democrat, strong"      = "Strong democrat")) %>% 
   group_by(partyid) %>%
   summarise(tvhours = mean(tvhours)) %>%
   ggplot(aes(tvhours, fct_reorder(partyid, tvhours))) +
     geom_point() + labs(y = "partyid")

```

## Your Turn 5

What is the best time of day to fly?

Use the `hour` and `minute` variables in `flights` to compute the time of day for each flight as an hms. Then use a smooth line to plot the relationship between time of day and `arr_delay`.

```{r}
## Your Turn 5
flights %>% 
  mutate(time = hms(hour = hour, minute = minute)) %>% 
  ggplot(aes(time, arr_delay)) + 
    geom_point(alpha = 0.2) + geom_smooth()

```

## Your Turn 6

Fill in the blanks to:

Extract the day of the week of each flight (as a full name) from `time_hour`. 

Calculate the average `arr_delay` by day of the week.

Plot the results as a column chart (bar chart) with `geom_col()`.

```{r}
## Your Turn 6
flights %>% 
  mutate(weekday = wday(time_hour, label = TRUE, abbr = FALSE)) %>% 
  group_by(weekday) %>% 
  drop_na(arr_delay) %>% 
  summarise(avg_delay = mean(arr_delay)) %>% 
  ggplot() +
    geom_col(mapping = aes(x = weekday, y = avg_delay))

```


*** 
## Appendix 1 - all code used in this training
```{r, ref.label=knitr::all_labels(),echo=TRUE, eval=FALSE}
```

***
## Appendix 2 - R Session Information

```{r}
sessionInfo()
```