---
title: "Iteration"
output:
  html_document:
    df_print: paged
    toc: TRUE
    toc_float: TRUE
    toc_depth: 4
    code_download: TRUE
---

```{r setup}
library(tidyverse)

# Toy data
set.seed(1000)
exams <- list(
  student1 = round(runif(10, 50, 100)),
  student2 = round(runif(10, 50, 100)),
  student3 = round(runif(10, 50, 100)),
  student4 = round(runif(10, 50, 100)),
  student5 = round(runif(10, 50, 100))
)

extra_credit <- list(0, 0, 10, 10, 15)
```

## Your Turn 1

Here is a list:

```{r}
## Your Turn 1
a_list <- list(num = c(8, 9), 
            log = TRUE,    
            cha = c("a", "b", "c"))
```

Here are two subsetting commands. Do they return the same values? Run the code chunk above, _and then_ run the code chunks below to confirm

```{r}
a_list["num"]
```

```{r}
a_list$num

```

## Your Turn 2

What will each of these return? Run the code chunks to confirm.

```{r}
## Your Turn 2
vec <- c(-2, -1, 0, 1, 2)
abs(vec)
```

```{r}
lst <- list(-2, -1, 0, 1, 2)
abs(lst)

```

## Your Turn 3

Run the code in the chunks. What does it return?

```{r}
## Your Turn 3
list(student1 = mean(exams$student1),
     student2 = mean(exams$student2),
     student3 = mean(exams$student3),
     student4 = mean(exams$student4),
     student5 = mean(exams$student5))
```

```{r}
map(exams, mean)

```

## Your Turn 4

Calculate the variance (`var()`) of each student’s exam grades.

```{r}
## Your Turn 4

```

## Your Turn 5

Calculate the max grade (max())for each student. Return the result as a vector.

```{r}
## Your Turn 5

```

## Your Turn 6

Write a function that counts the best exam twice and then takes the average. Use it to grade all of the students.

1. Write code that solves the problem for a real object  
2. Wrap the code in `function(){}` to save it  
3. Add the name of the real object as the function argument 

```{r}
## Your Turn 6

```

### Your Turn 7

Compute a final grade for each student, where the final grade is the average test score plus any `extra_credit` assigned to the student. Return the results as a double (i.e. numeric) vector.

```{r}
### Your Turn 7

```



*** 
## Appendix 1 - all code used in this training
```{r, ref.label=knitr::all_labels(),echo=TRUE, eval=FALSE}
```

***
## Appendix 2 - R Session Information

```{r}
sessionInfo()
```