---
title: "Models"
output:
  html_document:
    df_print: paged
    toc: TRUE
    toc_float: TRUE
    toc_depth: 4
    code_download: TRUE
---

```{r setup, message=FALSE}
library(tidyverse)
library(modelr)
library(broom)

wages <- heights %>% filter(income > 0)
```

## Your Turn 1

Fit the model on the slide and then examine the output. What does it look like?

```{r}
## Your Turn 1
mod_e <- wages %>%
  lm(log(income) ~ education, data = .)
```

## Your Turn 2

Use a pipe to model `log(income)` against `height`. Then use broom and dplyr functions to extract:

1. The **coefficient estimates** and their related statistics 
2. The **adj.r.squared** and **p.value** for the overall model

```{r}
## Your Turn 2
mod_h <- wages %>% lm(log(income) ~ height, data = .)
mod_h %>%
  tidy()

mod_h %>% 
  glance() %>% 
  select(adj.r.squared, p.value)

```

## Your Turn 3

Model `log(income)` against `education` _and_ `height`. Do the coefficients change?

```{r}
## Your Turn 3
mod_eh <- wages %>% 
  lm(log(income) ~ education + height, data = .)

mod_eh %>% 
  tidy()

```

## Your Turn 4

Model `log(income)` against `education` and `height` and `sex`. Can you interpret the coefficients?

```{r}
## Your Turn 4
mod_ehs <- wages %>% 
  lm(log(income) ~ education + height + sex, data = .)

mod_ehs %>% 
  tidy()

```

## Your Turn 5

Use a broom function and ggplot2 to make a line graph of `height` vs `.fitted` for our heights model, `mod_h`.

_Bonus: Overlay the plot on the original data points._

```{r}
## Your Turn 5
mod_h %>% 
  augment(data = wages) %>% 
  ggplot(mapping = aes(x = height, y = .fitted)) +
    geom_point(mapping = aes(y = log(income)), alpha = 0.1) +
    geom_line(color = "blue")

```

## Your Turn 6

Repeat the process to make a line graph of `height` vs `.fitted` colored by `sex` for model mod_ehs. Are the results interpretable? Add `+ facet_wrap(~education)` to the end of your code. What happens?

```{r}
## Your Turn 6
mod_ehs %>% 
  augment(data = wages) %>% 
  ggplot(mapping = aes(x = height, y = .fitted, color = sex)) +
    geom_line() +
    facet_wrap(~ education)

```

## Your Turn 7

Use one of `spread_predictions()` or `gather_predictions()` to make a line graph of `height` vs `pred` colored by `model` for each of mod_h, mod_eh, and mod_ehs. Are the results interpretable? 

Add `+ facet_grid(sex ~ education)` to the end of your code. What happens?

```{r warning = FALSE, message = FALSE}
## Your Turn 7
mod_h <- wages %>% lm(log(income) ~ height, data = .)
mod_eh <- wages %>% lm(log(income) ~ education + height, data = .)
mod_ehs <- wages %>% lm(log(income) ~ education + height + sex, data = .)

wages %>% 
  gather_predictions(mod_h, mod_eh, mod_ehs) %>% 
  ggplot(mapping = aes(x = height, y = pred, color = model)) +
    geom_line() +
    facet_grid(sex ~ education)

```

*** 
## Appendix 1 - all code used in this training
```{r, ref.label=knitr::all_labels(),echo=TRUE, eval=FALSE}
```

***
## Appendix 2 - R Session Information

```{r}
sessionInfo()
```
