---
title: "List-Columns"
output:
  html_document:
    df_print: paged
    toc: TRUE
    toc_float: TRUE
    toc_depth: 4
    code_download: TRUE
---

```{r setup, message=FALSE}
library(tidyverse)
library(broom)
library(gapminder)
library(stringr)

knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

## Your Turn 1

How has life expectancy changed since 1952?

Using `gapminder`, make a line plot of **lifeExp** vs. **year** grouped by **country**. Set alpha to 0.2, to see the results better.

```{r}
## Your Turn 1
gapminder %>% 
  ggplot(mapping = aes(x = year, y = lifeExp, group = country)) +
    geom_line(alpha = 0.2)

```

## Your Turn 2

1. Group `gapminder` by `country` and `continent` then fit a model and collect the residuals for *each country.*

2. Plot the residuals vs `year` as a line graph, grouped by `country`, with `alpha = 0.2`.

3. Add the following to your plot to facet by `continent`:

    + facet_wrap(~continent)

```{r warning = FALSE}
## Your Turn 2
gapminder %>% 
  group_by(country, continent) %>% 
  do(lm(lifeExp ~ year, data = .) %>%  augment()) %>%  
  ggplot() +
    geom_line(aes(year, .resid, group = country), alpha = 0.2) +
    facet_wrap(~continent)

```

## Your Turn 3

Complete the code to filter `residuals`, which is the dataset that you made in Your Turn 2, against `bad_fits`, which is the data set that contains just the countries that have an r-squared < 0.25.

Use the result to plot a line graph of `year` vs. `.resid` colored by `country` for each country that had an r-squared < 0.25.

```{r warning = FALSE}
## Your Turn 3
bad_fits <- gapminder %>% 
  group_by(country) %>% 
  do(lm(lifeExp ~ year, data = .) %>%  glance()) %>% 
  filter(r.squared < 0.25) 

residuals <- gapminder %>% 
  group_by(country) %>% 
  do(lm(lifeExp ~ year, data = .) %>%  augment()) 

residuals %>% 
  semi_join(bad_fits) %>% 
  ggplot() +
    geom_line(aes(year, .resid, color = country))


```

## Your Turn 4

Create your own copy of master and then add one more list column: 

* **output** which contains the output of `augment()` for each model

```{r warning = FALSE}
## Your Turn 4
fit_model <- function(df) lm(lifeExp ~ year, data = df)
get_rsq <- function(mod) glance(mod)$r.squared
get_output <- function(mod) augment(mod)


master <- gapminder %>% 
  group_by(country) %>% 
  nest() %>% 
  mutate(model = map(data, fit_model),
         r.squared = map_dbl(model, get_rsq),
         output = map(model, get_output))
master

```

## Your Turn 5

Use master to recreate our plot of the residuals vs `year` for the six countries with an r squared less than 0.25.

```{r}
## Your Turn 5
master %>%
  filter(r.squared < 0.25) %>%
  unnest(output) %>%
  ggplot() +
    geom_line(mapping = aes(x = year, y = .resid, color = country))

```


*** 
## Appendix 1 - all code used in this training
```{r, ref.label=knitr::all_labels(),echo=TRUE, eval=FALSE}
```

***
## Appendix 2 - R Session Information

```{r}
sessionInfo()
```