---
title: "Visualize Data - Test your knowledge"
output: html_notebook
---

```{r setup}
library(tidyverse)
```

# indomethacin concentration profiles
The following data shows PK concentration profiles for the drug indomethacin.
It has the following columns:  
  
  * Subject - an ordered factor with containing the subject codes. The ordering 
  is according to increasing maximum response.  
  * time - a numeric vector of times at which blood samples were drawn (hr).
  * conc - a numeric vector of plasma concentrations of indometacin (mcg/ml).
  
```{r}
head(Indometh)
```

## Test your knowledge - spaghetti plot
Create a "spaghetti plot" of indomethacin PK concentration profiles. I've provided
code statements that you may find useful. Fill in the blanks. Keep testing your
code until you get the desired plot.

```{r}
ggplot(data = Indometh) +
  geom_line(mapping = aes(x = , y = , group = )) + 
  labs(x = "time (hrs)",
       y = "concentration (ng/ml)",
       title = "indomethacin concentration profiles")
```

### Extra credit
Consult the "Data Visualization with ggplot2" Cheat Sheet to change the y-axis
to be on the log10 scale. It should be one line of code. Add this to the code 
above in the following chunk:

```{r}
ggplot(data = Indometh) +
  geom_line(mapping = aes(x = , y = , group = )) + 
  labs(x = "time (hrs)",
       y = "concentration (ng/ml)",
       title = "indomethacin concentration profiles") +
  
```


## Test your knowledge 2 - boxplots

Replace the scatterplot above with one that draws boxplots at each time point. 
Use the cheatsheet. Try your best guess.

```{r}
ggplot(data = Indometh) +
  geom_boxplot(mapping = aes(x = , y = , group = )) + 
  labs(x = "time (hrs)",
       y = "concentration (ng/ml)",
       title = "indomethacin concentration profiles")
```
