---
title: "Visualize Data - Test your knowledge"
output: html_document
---

```{r setup}
library(tidyverse)
```

# indomethacin concentration profiles
The following data shows PK concentration profiles for the drug indomethacin.
It has the following columns:  
  
  * Subject - an ordered factor with containing the subject codes. The ordering 
  is according to increasing maximum response.  
  * time - a numeric vector of times at which blood samples were drawn (hr).
  * conc - a numeric vector of plasma concentrations of indometacin (mcg/ml).
  
```{r}
head(Indometh)
```

## Test your knowledge - spaghetti plot
Create a "spaghetti plot" of indomethacin PK concentration profiles.
I've provided some code statements that you may find 
useful. Fill in the blanks. Keep testing your code until you get the desired plot.
Consult the "Data Visualization with ggplot2" Cheat Sheet to change the y-axis
to be on the log10 scale. It should be one line of code. 

Once you're happy with your plot, add axes labels and a title then save your 
plot as a `.png` file using the `ggsave` function.


```{r}
spagPlot <- ggplot(data = Indometh) +
  geom_line( mapping = aes(x =  , y =  , group =  ) )

spagPlot 

# ggsave( )
```

## Extra credit - add a summary to the above plot

Use the Cheat Sheet to identify how to add a summary statistic line to the plot.
A suitable example might be a median line, but you may also want to experiment
with median and quantiles or mean and standard errors. 

You can reuse the plot object from the chunk above as the starting point for the 
next graph. Simply refer to the `spagPlot` object then `+` new layers.

HINT: You may need to reconsider the grouping aesthetic for summaries.

```{r}
spagPlot + 

```


## Extra-extra credit - boxplots

Replace the spaghetti plot above with one that draws boxplots at each time point. 
Use the cheatsheet. Try your best guess.

```{r}

```

