---
title: "Visualize Data - Test your knowledge"
output: html_document
---

```{r setup}
library(tidyverse)
```

# indomethacin concentration profiles
The following data shows PK concentration profiles for the drug indomethacin.
It has the following columns:  
  
  * Subject - an ordered factor with containing the subject codes. The ordering 
  is according to increasing maximum response.  
  * time - a numeric vector of times at which blood samples were drawn (hr).
  * conc - a numeric vector of plasma concentrations of indometacin (mcg/ml).
  
```{r}
head(Indometh)
```

## Test your knowledge - spaghetti plot
Create a "spaghetti plot" of indomethacin PK concentration profiles and add
title and axes labels. I've provided some code statements that you may find 
useful. Fill in the blanks. Keep testing your code until you get the desired plot.
Consult the "Data Visualization with ggplot2" Cheat Sheet to change the y-axis
to be on the log10 scale. It should be one line of code. 

```{r}
ggplot(data = Indometh) +
  geom_line(mapping = aes(x = , y = , group = )) + 
  labs(x = ,
       y = ,
       title = ) + 
  
```

## Extra credit - boxplots

Replace the scatterplot above with one that draws boxplots at each time point. 
Use the cheatsheet. Try your best guess.

```{r}

```

