---
title: "Import Data (Bonus)"
output: html_notebook
---

```{r setup}
library(tidyverse)
```

This module will teach you an efficient way to import data stored in a flat file format. Flat file formats are one of the most common formats for saving data because flat files can be read by a large variety of data related software. Flat file formats include Comma Separated Values (csv's), tab delimited files, fixed width files and more.

## readr

The **readr** R package contains simple, consistent functions for importing data saved as flat file documents. readr functions offer an alternative to base R functions that read in flat files. Compared to base R's `read.table()` and its derivatives, readr functions have several advantages. readr functions:

* are ~10 times faster
* return user-friendly tibbles
* have more intuitive defaults. No rownames, no `stringsAsFactors = TRUE`.

readr supplies several related functions, each designed to read in a specific flat file format. 

Function       | Reads
-------------- | --------------------------
`read_csv()`   | Comma separated values
`read_csv2()`  | Semi-colon separate values
`read_delim()` | General delimited files
`read_fwf()`   | Fixed width files
`read_log()`   | Apache log files
`read_table()` | Space separated files
`read_tsv()`   | Tab delimited values

Here, we will focus on the `read_csv()` function, but the other functions work in a similar way. In most cases, you can use the syntax and arguments of `read_csv()` when using the other functions listed above.

readr is a core member of the tidyverse. It is loaded everytime you call `library(tidyverse)`.


## Tibbles

`read_csv()` reads the data into a **tibble**, which is a special class of data frame. Since a tibble is a sub-class of data frame, R will in most cases treat tibbles in exactly the same way that R treats data frames.

tibble is a core member of the tidyverse. It is loaded everytime you call `library(tidyverse)`. The tibble package includes the functions `tibble()` and `tribble()` for makign tibbles from scratch, as well as `as_tibble()` and `as.data.frame()` for converting back and forth between tibbles and data frames.

In almost every case, you can ignore whether or not you are working with tibbles or data frames.

### Creating datasets on the fly with `tribble()`

You can create datasets in your code using the `tribble` function.
These are really useful if you need a quick illustrative dataset or
to carry out a quick test of code or function.

```{r}
tribble(
  ~colA,    ~colB,
  "apple",    1,
  "banana",   2,
  "cucumber", 3
)
```

## Sample data

In this course, we're using a publically available dataset on depression.
The data is from https://missingdata.lshtm.ac.uk/category/dia-working-group/example-data-sets/ (Website accessed 25 Nov 2019).
The associated manuscript is https://www.ncbi.nlm.nih.gov/pubmed/15232330.

The dataset records depression score data on individual patients across time.
A feature of the data is that some individuals have missing scores.

## Importing Data

To import `chapter15_example2.csv`, use the readr functions that reads `.csv` files, `read_csv()`. Set the first argument of `read_csv()` to a characterstring: the filepath from your _working directory_ to the `chapter15_example2.csv` file.

## Your turn 1
Add the appropriate arguments to the `read_csv` function below to read in `chapter15_example2.csv`. Use the TAB key to browse the arguments, alternatively read the CheatSheet or visit https://readr.tidyverse.org/reference/read_delim.html for
more detail on the function.

```{r eval = FALSE}
depression <- read_csv(  )
depression
```

Note: you can determine the location of your working directory by running `getwd()`. You can change the location of your working directory by going to **Session > Set Working Directory** in the RStudio IDE menu bar.

Notice the messages from `read_csv()`. Check that the data column types match your expectations and what you see in the dataset itself.

Notice that the code above saves the output to an object named depression. You must save the output of `read_csv()` to an object if you wish to use it later. If you do not save the output, `read_csv()` will merely print the contents of the data set at the command line.

## Parsing NA's

If you examine `depression` closely, you will notice that the initial values in the `HAMDTL17` column are `.`. Can you guess what `.` stands for? The compilers of the data set used `.` to denote a missing value. In other words, they used `.` in the same way that R uses the `NA` value. 

If you'd like R to treat these `.` values as missing values (and you should) you will need to convert them to `NA`s. One way to do this is to ask `read_csv()` to parse `.` values as `NA` values when it reads in the data. To do this add the argument `na = "."` to `read_csv()`:

```{r eval = FALSE}
depression <- read_csv("chapter15_example2.csv", na = ".")
```

You can set `na` to a single character string or a vector of character strings. `read_csv()` will transform every value listed in the `na` argument to an `NA` when it reads in the data.

## Parsing data types

If you run the code above and examine the results, you may now notice a new concern about the `PGIIMP` column. The column has been parsed as character strings instead of numbers. 

When you use `read_csv()`, `read_csv()` tries to match each column of input to one of the basic data types in R. `read_csv` generally does a good job, but here the initial presence of the character strings `NA` caused `read_csv()` to misidentify the contents of the `PGIIMP` column. You can now correct this with R's `as.numeric()` function, or you can read the data in again adding "NA" to the set of strings denoting missingness, this time instructing `read_csv()` to parse the column as numbers.

To do this, add the argument `col_types` to `read_csv()` and set it equal to a list. Add a named element to the list for each column you would like to manually parse. The name of the element should match the name of the column you wish to parse. 

```{r eval = FALSE}
## Fill in column name(s) and data parse types based on information from the CheatSheet
depression <- read_csv("chapter15_example2.csv", na = ".",
                   col_types = list(  =  ))
                                      
## Fill in the y-axis variable to plot the data
plot1 <- depression %>% 
  ggplot(mapping = aes(x = RELDAYS, y =  , 
															group = PATIENT)) +
		 geom_line(alpha=0.2)
plot1
```

To complete the code, set `PGIIMP` equal to one of the functions below, each function instructs `read_csv()` to parse `chapter15_example2.csv` as a specific type of data.

Type function     | Data Type
----------------- | -----------------------------------------
`col_character()` | character
`col_date()`      | Date
`col_datetime()`  | POSIXct (date-time)
`col_double()`    | double (numeric)
`col_factor()`    | factor
`col_guess()`     | let readr geuss (default)
`col_integer()`   | integer
`col_logical()`   | logical
`col_number()`    | numbers mixed with non-number characters
`col_numeric()`   | double or integer
`col_skip()`      | do not read this column
`col_time()`      | time

In our case, we could use the `col_integer()` function to ensure that `PGIIMP` is read as an integer numeric column.

## Writing data

readr also contains functiomns for saving data. These functions parallel the read functions and each save a data frame or tibble in a specific file format.

Function            | Writes
------------------- | ----------------------------------------
`write_csv()`       | Comma separated values
`write_excel_csv()` | CSV that you plan to open in Excel
`write_delim()`     | General delimited files
`write_file()`      | A single string, written as is
`write_lines()`     | A vector of strings, one string per line
`write_tsv()`       | Tab delimited values

To use a write function, first give it the name of the data frame to save, then give it a filepath from your working directory to the location where you would like to save the file. This filepath should end in the name of the new file. So we can save the clean `depression` data set as a csv in our working directory with 

```{r eval = FALSE}
write_csv(depression, path = "depression.csv")
```

## Reading SAS data

Now that we've learned how to import .csv files, we can go on to look at other data formats. The patterns are very similar.

```{r}
library(haven)
read_sas("chapter15_example.sas7bdat")
```

## Reading Excel files

Similarly, we can read (and write) data directly from and to Excel .xlsx files. Here we're specifying a range that will select a subset of the full data from the Excel file.

```{r}
library(readxl)
read_excel("chapter15_example.xlsx", sheet = "chapter15_example", range = "A1:J47")
```

We can write this (subset) back to a new Sheet in the Excel file. This uses the 
`openxlsx` package

```{r}
library(openxlsx)
## Write out data
write.xlsx(x = depression, file = "depression.xlsx")

wb <- createWorkbook(title = "Depression Data")
addWorksheet(wb, sheetName = "Data")
writeData(wb, sheet = "Data", x = depression)
saveWorkbook(wb, "depression.xlsx", overwrite = TRUE)

addWorksheet(wb, sheetName = "Graph")
plot1
insertPlot(wb = wb,sheet = "Graph")
saveWorkbook(wb, "depression.xlsx", overwrite = TRUE)
```

## Using rvest to scrape data from websites
`rvest` is very useful if you need to scrape data from a website. The `read_html` function will read and parse the HTML code from the website, but from there you need to rely on identifying relevant parts of the HTML code
to pick up the data of interest. If you can access web data via an API then the `httr` package or the `polite` package (https://dmi3kno.github.io/polite/) will do better. 

```{r}
library(rvest)

sayCheese <- read_html("https://cheese.com/by_type/?t=semi-soft")

sayCheese %>%
  html_node("#main-body") %>% 
  html_nodes("h3") %>% 
  html_text()
```

## datapasta - Creating data from clipboard
`datapasta` is a useful RStudio IDE addin that allows you to copy rectangular data (from PDFs, websites and other sources) then choose how you want to "paste" that data, either creating an object on the fly, or by writing a `tribble` statement for inclusion in a script or Notebook.

***(UNFORTUNATELY datapasta DOESN'T WORK ON RSTUDIO.CLOUD)***

Try it by visiting: https://cran.r-project.org/web/packages/datapasta/vignettes/how-to-datapasta.html and copying the Brisbane weather data from the table into the clipboard. Then using the "Addins" dropdown menu above,
paste it into the chunk below as a tribble.

```{r}

```

***

# Take Aways

The readr package provides efficient functions for reading and saving common flat file data formats.

Consider these packages for other types of data:

Package  | Reads
-------- | -----
haven    | SPSS, Stata, and SAS files
readxl   | excel files (.xls, .xlsx)
jsonlite | json
xml2     | xml
httr     | web API's
rvest    | web pages (web scraping)
DBI      | databases
sparklyr | data loaded into spark
