---
title: "Writing functions with RStudio IDE"
output: html_notebook
---

The RStudio IDE really helps you write functions. Let's start with the familiar
example dataset from the `06-Iteration.Rmd` document.

```{r}
# Toy data
set.seed(1000)
exams <- list(
  student1 = round(runif(10, 50, 100)),
  student2 = round(runif(10, 50, 100)),
  student3 = round(runif(10, 50, 100)),
  student4 = round(runif(10, 50, 100)),
  student5 = round(runif(10, 50, 100))
)
```

Now let's write a function that will compute the average, excluding the lowest 
score. First, let's write the function out using a single vector of data from
the `exams` list. This lets us test that the function is well defined and gives 
us the result we're expecting.

```{r calculate_new_average}
(sum(exams$student1) - min(exams$student1)) / (length(exams$student1) - 1)
```

Now, highlight the single line of code above and from the "Code" menu in the 
RStudio IDE, select "Extract function". This will prompt you to give the function
a name. What you get back is a defined function, and RStudio will guess what the
most appropriate inputs are.

**QUESTION** - What do you think the input is to your new function?  How could
we change this so that it applies to a vector, rather than a list input?

Repeat the same exercise (Code -> Extract function) on the code below (highlight
only the line with `(sum(x) - min(x)...)`). Check that this function works 
for the different values of x.

```{r}
x <- exams$student1

(sum(x) - min(x)) / (length(x) - 1)

```

## Troubleshooting and debugging functions.
When you write a more complex function it can sometimes be difficult to 
troubleshoot and debug when things go wrong. This is especially true if you 
have many arguments to the function.

But do not fear! RStudio IDE has a bunch of useful functionality that will help
you step through functions - even functions that call functions - to get to 
the bottom of what's going wrong.