---
title: "Master the tidyverse - Final Exam"
author: "Mike K Smith"
date: "18/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## What is this "Final Exam"?

While I'm calling this the "Final Exam" for the "Master the Tidyverse" course,
I am not going to grade the returned markdown documents, nor am I going to be
awarding "Certified" status for the course based on your response. 
The "Exam" here is to help you check your own understanding of the course 
material and to encourage you to try out the methods and tools you have learned 
on some real data.

## What is the data?

In this folder you'll find (**anonymised!**) attendance data across the sessions
we have run for this "Master the tidyverse" course. 

```{r}
read_csv("AttendanceDetailReport_185138_511218795_Anonymised.csv") %>%
  head()
```

You'll see information about the event scheduled start and end dates and times,
actual start and end times, whether the attendee was a panellist or a regular
attendee; then for each `attendeeID` what time they joined the call, what time they
left the call and duration information. Note that each `attendeeID` might have 
multiple joining and leaving times since they might start the call on a mobile 
phone and then transfer to a desktop machine for the call when they reach the
office.

## What would I like you to do?

I would like you to read the data, process and tidy the information, and present
some insight about the following aspects:

  * The number of distinct attendees across sessions
  * How many attendees came to all sessions?
  * How long did attendees spend at each session (total) and what is the 
  distribution of attendance within each session i.e. if we sum the amount of 
  time spent in the session for each attendeeID.
  * Which sessions were more popular?
  * Think about a visual way(s) to present some of this information.

Extra credit:

  *  Is there a way to classify attendees as having "completed"
  the session i.e. a duration which separates those that attend the majority of
  the session compared to those that drop off / drop out of each session?
  
Present your insights in a Report using rmarkdown to gather your code and results.

## Getting started:

I'm including a little snippet of code to help you get started. You should 
expand on this to ensure that the information you are reading in is parsed 
correctly e.g. with dates, times, durations.

```{r}
inFiles <- tools::list_files_with_exts(dir = file.path(getwd()),
                                        exts = "csv")

readMyCSV <- function(x){
  myData <- readr::read_csv(x)
  # ...
}

myData <- inFiles %>%
  purrr::map(readMyCSV) 
```

